\documentclass[12pt]{article}


\begin{document}

2002

\nocite{2002_aero_pulse}

NONLINEAR NMR IN A SUPERFLUID B PHASE OF 3HE IN AEROGEL
Dmitriev V.V., Zavjalov V.V., Zmeev D.E., Kosarev I.V., Mulders N.
Journal of Experimental and Theoretical Physics Letters (JETP Letters). 2002. Т. 76.  5. С. 312-317. 	17

Dmitriev V.V., Zavjalov V.V., Zmeev D.E., Kosarev I.V., Mulders N.
Journal of Experimental and Theoretical Physics Letters (JETP Letters). 2002. Т. 76. С. 321. 	5

Dmitriev V.V., Zavjalov V.V., Zmeev D.E., Kosarev I.V., Mulders N.
Journal of Experimental and Theoretical Physics Letters (JETP Letters). 2002. Т. 76. С. 371. 	1

Dmitriev V.V., Zavjalov V.V., Zmeev D.E., Kosarev I.V., Mulders N.
Письма в "Журнал экспериментальной и теоретической физики". 2002. Т. 76. С. 371. 	13

2003

PULSED NMR EXPERIMENTS IN SUPERFLUID 3HE CONFINED IN AEROGEL
Dmitriev V.V., Kosarev I.V., Zavjalov V.V., Zmeev D.Ye., Mulders N.
Physica B: Condensed Matter. 2003. Т. 329-333. С. 296-298. 	7

EXPERIMENTS ON A-LIKE TO B PHASE TRANSITIONS OF 3HE CONFINED TO AEROGEL
Dmitriev V.V., Kosarev I.V., Zavjalov V.V., Zmeev D.Ye., Mulders N.
Physica B: Condensed Matter. 2003. Т. 329-333. С. 320-321. 	18

MEASUREMENTS OF LONGITUDINAL AND TRANSVERSE MAGNETIC RELAXATION IN SUPERFLUID 3HE CONFINED TO AEROGEL
Dmitriev V.V., Kosarev I.V., Zavjalov V.V., Zmeev D.Ye., Mulders N.
Physica B: Condensed Matter. 2003. Т. 329-333. С. 322-323. 	4

HOMOGENEOUS SPIN PRECESSION IN SUPERFLUID 3HE CONFINED TO AEROGEL
Dmitriev V.V., Kosarev I.V., Zavjalov V.V., Zmeev D.Ye., Mulders N.
Physica B: Condensed Matter. 2003. Т. 329-333. С. 324-326. 	1

Dmitriev V.V., Kosarev I.V., Mulders N., Zavjalov V.V., Zmeev D.E.
Physica B: Condensed Matter. 2003. Т. 320. С. 329. 	1

Дмитриев В.В., Завьялов В.В., Змиев Д.Е.
Успехи физических наук. 2003. Т. 173.  4. С. 452. 	2

Dmitriev V.V., Zavjalov V.V., Zmeev D.E., Kosarev I.V., Mulders N.
Письма в "Журнал экспериментальной и теоретической физики". 2003. Т. 79. С. 612. 	1

Выставкин А.Н., Дмитриев В.В., Завьялов В.В., Коваленко А.Г., Ковтонюк С.А., Чеботарев А.А.
Радиотехника и электроника. 2003. Т. 48.  7. С. 874. 	4

SUPERFLUID PHASES OF3HE IN AEROGEL
Dmitriev V.V., Zav'yalov V.V., Zmeev D.E., Kosarev I.V., Mulders N.
Physics-Uspekhi. 2003. Т. 46.  4. С. 438-442. 	0

 2004

PURIFICATION OF 3HE FROM A 4HE IMPURITY USING ADSORPTION
Dmitriev V.V., Zavjalov V.V., Zmeev D.Y., Levitin L.V.
Instruments and Experimental Techniques. 2004. Т. 47.  4. С. 567-569. 	1

MEASUREMENT OF THE LEGGETT FREQUENCY IN 3HE-B IN AEROGEL
Dmitriev V.V., Zavjalov V.V., Zmeev D.Ye., Mulders N.
Journal of Experimental and Theoretical Physics Letters (JETP Letters). 2004. Т. 79.  10. С. 499-503. 	9

Dmitriev V.V., Mulders N., Zavjalov V.V., Zmeev D.E.
Письма в "Журнал экспериментальной и теоретической физики". 2004. Т. 79. С. 612. 	4

PURIFICATION OF 3HE FROM A 4HE IMPURITY USING ADSORPTION
Dmitriev V.V., Zav'yalov V.V., Zmeev D.E., Levitin L.V.
Приборы и техника эксперимента. 2004.  4. С. 160-162. 	0


 2005

\nocite{2005_he3b_hpd_osc}

SEPARATION OF 3HE FROM 3HE-4HE MIXTURE BY MEANS OF ADSORPTION
Dmitriev V.V., Levitin L.V., Zavjalov V.V., Zmeev D.Ye.
Journal of Low Temperature Physics. 2005. Т. 138.  3-4. С. 877-880. 	1

 2006

\nocite{2004_aero_btext}

CW NMR MEASUREMENTS OF THE LEGGETT FREQUENCY IN 3HE-B IN AEROGEL
Dmitriev V.V., Zavjalov V.V., Zmeev D.E., Mulders N.
В сборнике: AIP Conference ProceedingsLOW TEMPERATURE PHYSICS: 24th International Conference on Low Temperature Physics - LT24. Сер. "LOW TEMPERATURE PHYSICS: 24th International Conference on Low Temperature Physics - LT24" Orlando, FL, 2006. С. 229-230. 	5

 2007

TRANSVERSE AND LONGITUDINAL NUCLEAR MAGNETIC RESONANCE IN SUPERFLUID 3HE IN ANISOTROPIC AEROGEL
Dmitriev V.V., Krasnikhin D.A., Zavjalov V.V., Zmeev D.E., Mulders N.
Journal of Experimental and Theoretical Physics Letters (JETP Letters). 2007. Т. 86.  9. С. 594-599. 8

TRANSVERSE AND LONGITUDINAL NUCLEAR MAGNETIC RESONANCE IN SUPERFLUID 3HE IN ANISOTROPIC AEROGEL
Dmitriev V.V., Krasnikhin D.A., Mulders N., Zavjalov V.V., Zmeev D.E.
Письма в "Журнал экспериментальной и теоретической физики". 2007. Т. 86.  9. С. 681-687. 5


\bibliography{mybib}
\bibliographystyle{plain}

\end{document}